### 2017-03-20 Manuscript/SW_early_life_telomeres_SOM.Rmd
MAJOR EDITS
Changed to pdf format

---
output:
  word_document:
    reference_docx: myref.docx
---

###Supplementary information for Spurgin *et al.* "Spatiotemporal variation in lifelong telomere dynamics in a long-term ecological study"

@@

#Set some options
options(na.action='na.fail')
opts_knit$set(root.dir = '..')
opts_chunk$set(echo=FALSE,
               warning=FALSE,
               message=FALSE,
               fig.path='../Figures/',
               fig.width= 5,
               fig.height= 5,
               fig.show='asis',
               dev=c('png'))

@@

**Table S2** Full model of factors affecting $\Delta$RTL in Seychelles warblers, using longitudinal data.
```{r Table S2}

@@

>>>>

---
output: pdf_document
classoption: landscape
---

#Supplementary information for Spurgin *et al.* "Spatiotemporal variation in lifelong telomere dynamics in a long-term ecological study"

@@

#Set some options
options(na.action='na.fail')
opts_knit$set(root.dir = '..')
opts_chunk$set(echo=FALSE,
               warning=FALSE,
               message=FALSE,
               fig.path='../Figures/',
               fig.width= 5,
               fig.height= 5)

@@

\pagebreak

**Table S2** Full model of factors affecting $\Delta$RTL in Seychelles warblers, using longitudinal data.

```{r Table S2}

@@

\pagebreak
